Nanophotonic Computational Design

### 2013-02-24 defense/pres3.tex
Basically done with defense presentation.

% \usepackage{pause}
\usepackage[display]{texpower}

@@

\oursection{Result 7: 4x4 hub}
\threeDfig{3Db_hub_4x4}
\I  Pop quiz: Can you guess which trace goes where?
\nextpage

@@

\I  \bold{Result}: Stable over $> 900$K thermal shifts
\threeDfig{analysis_temp_shift2}
\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
\I  Potentially means that networks with no need for thermal tuning are possible
    \BI Occurs when thermal robustness $>$ thermal swing \EI
\nextpage

@@

\I  \bold{Result}: Stable to $\sim$8 nm over-/under-etch 
\threeDfig{analysis_fab_shift2}
\I  Wavelength adjustment not needed in this case
\I  \bold{Key}: Shows that robustness to variation in wavelength 
    is a good heuristic for thermal and fabrication robustness
    \BI Designs using thermal and fabrication supermodes also possible\EI
\EI
\end{document}

>>>>

% \usepackage{pause}
\usepackage[display]{texpower} % For presentation
% \usepackage[printout]{texpower} % For print-out

@@

\oursection{Result 7: 4x4 hub}
\threeDfig{3Db_hub_4x4}
\I  Pop quiz: Can you tell which trace goes where?
\nextpage

@@

\I  \bold{Result}: Stable wavelengths available even up to $905$K shifts!
\threeDfig{analysis_temp_shift2}
\pause
\I  $\Delta T = 905$K point marks refractive index shift from 3.5 to 3.67 (huge!)
\pause
\I  Potentially means that networks with no need for thermal tuning are possible
    \BI Occurs when thermal robustness $>$ thermal swing \EI
\nextpage

@@

\I  \bold{Result}: Stable to $\sim$8 nm over-/under-etch 
\threeDfig{analysis_fab_shift2}
\I  Wavelength adjustment not needed in this case
\pause
\I  \bold{Key}: Shows that robustness to variation in wavelength 
    is a good heuristic for thermal and fabrication robustness
    \BI Designs using thermal and fabrication supermodes also possible\EI
\nextpage

\I  Robustness likely due to a combination of 
    small device footprint,
    broadband wavelength response, and
    low-intensity field in device
\medfig{top_wdm}
\nextpage

\oursection{Conclusion}
\footnotetext{$^\ast$maybe}
\I  How to design any$^\ast$ linear multi-mode nanophotonic device
    \BI using the full parameter space
    \I  simply by describing its operation \EI
\pause
\I  Our method results in designs which are
    \BI extremely compact
    \I  manufacturable \EI
\pause
\I  Devices can be designed which are robust to
    \BI wavelength shifts
    \I  thermal shifts 
    \I  fabrication error \EI
\oursection{Acknowledgements}
\begin{quote}
Not unto us, O Lord, not unto us, \\
But to Your name give glory, \\
Because of Your mercy, \\
Because of Your truth. (Psalm 115:1)
\end{quote}
\stepwise{
\step{Mom, Dad, }
\step{Jennifer, }
\step{Eli, }
\step{Seth, Lieven, Kelley,}
\step{Shanhui, Mark,}
\step{David,}
\step{Jelena,}
\step{Stephen,}
\step{Maria, Yiyang, Szu-lin, Gary,}
\step{JVgroup,}
\step{Owen, Paul,}
\step{Wonseok,}
\step{Ingrid,}
\step{Church family,}
\step{Sandy, Josiah}

\step{\begin{center}Thank you\end{center}}
}
\EI
\end{document}
